---
title: "Feature Selection for Spam Database"
author: "Ali & Zahra"
date: "Monday, April 27, 2015"
output: html_document
---

Here using the FSelector package, we want to find the most important attributes in the spam database.
The criteria is the information gain approach: we choose the most informative inputs.
Then we pick onlu 9 most important values, for training purposes:

```{r,echo=FALSE}
library('FSelector')
################################
######## WE USE ONLY the FIRST 2000 SAMPLES ###################
spam_data<-read.csv(
"D:/LSU/Spring 2015/Machine Learning/Project/R/spamtable.csv")
input<-spam_data[,1:57]
output<-spam_data[,58]
######################################
train.input<-input[1:2000,]
train.output<-output[1:2000]
##############################################
######### ASSIGNING NAMES ############################
train<-cbind(train.input,train.output)
colnames(train)<-c("V1","V2","V3","V4","V5","V6","V7","V8",
"V9","V10","V11","V12","V13","V14","V15","V16","V17","V18","V19","V20",
"V21","V22","V23","V24","V25","V26","V27","V28","V29","V30","V31","V32",
"V33","V34","V35","V36","V37","V38","V39","V40","V41","V42","V43","V44",
"V45","V46","V47","V48","V49","V50","V51","V52","V53","V54","V55","V56",
"V57","V58")
####################################################3
##### USING INFORMATON GAIN TO FIND 10 MOST IMPORTANT INPUTS ################
importance <- information.gain(V58~.,train)
#print(importance)
best.attributes <- cutoff.k(importance,10)
print(best.attributes)
f <- as.simple.formula(best.attributes, "V58")
print(f)
```


Let's try to see if we have similar results if we use gain ratio:

```{r,echo=FALSE}
importance <- gain.ratio(V58~.,train)
#print(importance)
best.attributes <- cutoff.k(importance,10)
print(best.attributes)
f <- as.simple.formula(best.attributes, "V58")
print(f)
```

We use the subset selected in gain ratio approach to train our methods


